Batch Bayesian Optimization via Multi-objective Acquisition Ensemble for Automated Analog Circuit Design

### 2018-06-05 paper/experiments.tex
Paper update
Add github address in the paper

The proposed MACE algorithm was tested using eight benchmark functions and two
real-world analog circuits. Four state-of-the-art parallel Bayesian optimization
methods were compared, including the BLCB
algorithm~\cite{desautels2014parallelizing}, the local penalization method with
EI acquisition function (EI-LP)~\cite{gonzalez2016batch}, the qEI and qKG
methods~\cite{qEI,wu2016parallel}\footnote{We implemented the BLCB algorithm as
the available open source implementations only allow discrete input. For the
EI-LP method, the code is downloaded from
https://github.com/SheffieldML/GPyOpt. The code for qEI and qKG is downloaded
from https://github.com/wujian16/Cornell-MOE}.

>>>>

The proposed MACE algorithm was tested using eight benchmark functions and two
real-world analog circuits. Four state-of-the-art parallel Bayesian optimization
methods were compared, including the BLCB
algorithm~\cite{desautels2014parallelizing}, the local penalization method with
EI acquisition function (EI-LP)~\cite{gonzalez2016batch}, the qEI and qKG
methods~\cite{qEI,wu2016parallel}. \footnote{We implemented the BLCB algorithm as
the available open source implementations only allow discrete input. For the
EI-LP method, the code is downloaded from
https://github.com/SheffieldML/GPyOpt. The code for qEI and qKG is downloaded
from https://github.com/wujian16/Cornell-MOE}.The code of our MACE algorithm is available at \texttt{https://github.com/Alaya-in-Matrix/MACE}.
